Generate data for multispecies modeling, including diet!

### 2020-10-21 NOBAmsdiets.Rmd
corrected labels, add fishery lenage, nageplot

##### `r names(survObsBiom)[1]`
``` {r}
map(survObsBiom$BTS_spring_allbox_effic1, plotB)[[1]]
```

##### `r names(survObsBiom)[2]`
```{r}
map(survObsBiom$BTS_fall_allbox_effic1, plotB)[[1]]
```

@@

#read in comp data
age_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsAgeComp.rds")))
age_comp_data <- age_comp_data[[1]]

Natage <- filter(age_comp_data, time %in% c(150:270))

@@

>>>>

##### `r names(survObsBiom)[1]`
``` {r}
map(survObsBiom$BTS_fall_allbox_effic1, plotB)[[1]]
```

##### `r names(survObsBiom)[2]`
```{r}
map(survObsBiom$BTS_spring_allbox_effic1, plotB)[[1]]
```

@@

#read in comp data--now done above with function
# age_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsAgeComp.rds")))
# age_comp_data <- age_comp_data[[1]]

#Natage <- filter(age_comp_data, time %in% c(150:270))

Natageplot <- <- function(dat){
  ggplot(dat, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          dat$species)) + 
    facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
}

#Natageplot 
```

@@

#### Fishery length composition
``` {r}
lcompsub <- as.data.frame(fish_len_comp_data) %>% filter(time %in% c(55:175)) %>%
  group_by(species) %>%
  group_map(~ plotlen(.x), keep = TRUE)
